From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-28 paper.tex
Put Severin as first author, to reflect the actual writing of the article

\title{From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction}
\author{Fernando Garcia \qquad Séverin Lemaignan \qquad Alexis Jacq \qquad Pierre Dillenbourg\\Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)\\École Polytechnique Fédérale de Lausanne (EPFL)}

>>>>

\title{From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction}
\author{Séverin Lemaignan \qquad Fernando Garcia \qquad Alexis Jacq \qquad Pierre Dillenbourg\\Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)\\École Polytechnique Fédérale de Lausanne (EPFL)}
